\LARGE \bf Mean Estimation from One-Bit Measurements

### 2020-12-09 conclusions.tex
removed last paragraph
fixed typos in the proof of Lemma 22

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that, asymptotically, no estimator can be more efficient than the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. Furtheremore, we showed that only one round of adapticity is required to attain the optimal efficiecny. In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
Under local asymptotic normality, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained in a distributed manner by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk. \par
Obvious extensions of our work include the derviation explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector. Another possible extension may consider estimation when single bits are sent between nodes of a directed graph.

>>>>

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that, asymptotically, no estimator can be more efficient than the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. Furthermore, we showed that only one round of adaptivity is required to attain optimal efficiency. In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
Under local asymptotic normality, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained in a distributed manner by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk. 
%
%\par
%Obvious extensions of our work include deriving explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector. Another possible extension may consider the efficiency of estimation when single bits are sent between nodes of a directed graph.

### 2020-12-09 distributed-estimation.tex
fixed typos in the proof of Lemma 22

%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$. However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space. As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.

@@

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

>>>>

%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$. However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space. As we shall see next, messages obtained via comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.

@@

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under the adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed-form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

### 2020-12-09 proof-lan-distributed.tex
removed Assumption A(ii) from Lemma 21
fixed typos in the proof of Lemma 22

We begin with an argument on the smoothness properties of the densities,
which is important for our Taylor expansions to come.
\begin{lemma}
  \label{lemma:derivative-bounds}
  Let
  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
  and \eqref{item:finite-intervals} hold. Then for any $A = \cup_{i = 1}^k
  \{[a_i, b_i]\}$ and $h \in \R$,
  \begin{equation*}
    P_{\theta + h}(A) = P_\theta(A) + \dPtheta(A) h \pm
    k \cdot \lip(f) h^2,
  \end{equation*}
  where
  \begin{equation}
    \dPtheta(A) = \sum_{i = 1}^k f(a_i - \theta) - f(b_i - \theta).
    \label{eqn:expansion-dPtheta}
  \end{equation}
  Additionally, we have the bounds
  \begin{equation}
    \label{eqn:bound-density-diffs}
    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}
    ~~ \mbox{and} ~~
    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}.
  \end{equation}
\end{lemma}
\noindent
See Section~\ref{sec:proof-derivative-bounds} for a proof.

@@

For shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
P_\theta$, and let $p_n, p$ be shorthand for the p.m.f.s of the two
distributions.  For the sets $A_i$ we recall that $B_i = \indic{X_i \in
  A_i}$.  The random variables
\begin{equation*}
  W_{n,i} \defeq 2 \left(\sqrt{\frac{p_n}{p}}(B_i) - 1\right)
\end{equation*}
are with $P$-probability 1 well-defined, and by the
inequalities~\eqref{eqn:h-fourth}, we have
that
\begin{align}
  \lefteqn{\var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
    \le 
    C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
      + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \cdot \frac{h_n^4}{n^2}
    + C \frac{k^4 \lip^4(f)}{
      P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{h_n^8}{n^4}} \nonumber \\
  & \qquad\qquad\qquad\qquad\qquad \le 
  C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
  \cdot \frac{h^4}{n^2}
  + C \frac{k^4 \lip^4(f)}{
    P_\theta(A_i)^3 P_\theta(A_i^c)^3}
  \frac{h^8}{n^4}
  \label{eqn:var-wni-expansion}
\end{align}
whenever
\begin{equation*}
  \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
  \score_\theta(A_i^c)\}
  \le \frac{1}{4}
  ~~ \mbox{and} ~~
  \frac{k_i h^2}{n} \lip^2(f)
  \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
\end{equation*}
Now, we use
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
coupled with Lemma~\ref{lemma:derivative-bounds} to show that the summed
variances converge to zero.  Indeed, Lemma~\ref{lemma:derivative-bounds} and
inequality~\eqref{eqn:var-wni-expansion} give that
\begin{equation*}
  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  \le C \cdot
  \left[\frac{k_i^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i^4}{P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{1}{n^3}\right] \frac{1}{n},
\end{equation*}
where $C < \infty$ depends only on $\lip(f)$ and $h$ (both of which are
uniformly bounded) whenever
\begin{equation*}
  \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)} \frac{1}{n} \le
  \frac{1}{C}.
\end{equation*}
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}
thus implies that $\E[\score_\theta(B_i)] = 0$ and
\begin{equation}
  \label{eqn:summed-variances-to-zero}
  \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  \to 0.
\end{equation}

@@

Now, we write the log-likelihood ratio. We have
\begin{align*}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  & = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
  & = \sum_{i = 1}^n W_{n,i}
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
  + \half \sum_{i = 1}^n W_{n,i}^2 R(W_{n,i})
\end{align*}
where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
Using the Taylor expansions of $\sqrt{\cdot}$ and
Lemma~\ref{lemma:derivative-bounds}, we have
\begin{align}
  \nonumber
  \half W_{n,i}
  & = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}}
  \pm \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
  + \frac{h_n^2}{n} \score_\theta(B_i)^2
  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
  & \in \pm
  C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right| \to 0,
  \label{eqn:max-wni-zero}
\end{align}
where $C < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
uniformly bounded;
the limit follows from Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}.
Consequently $\max_i W_{n,i} \to 0$, so that
\begin{equation}
  \label{eqn:almost-at-the-end}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
\end{equation}

>>>>

We begin with an argument on the smoothness properties of the densities,
which is important for our Taylor expansions to come.
\begin{lemma}
  \label{lemma:derivative-bounds}
  Let
  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
%  and \eqref{item:finite-intervals} 
 hold. Then for any $A = \cup_{i = 1}^k
  \{[a_i, b_i]\}$ and $h \in \R$,
  \begin{equation*}
    \left|P_{\theta + h}(A) - P_\theta(A) - \dPtheta(A) h \right| \leq 
    k \cdot \lip(f) h^2,
  \end{equation*}
  where
  \begin{equation}
    \dPtheta(A) = \sum_{i = 1}^k f(a_i - \theta) - f(b_i - \theta).
    \label{eqn:expansion-dPtheta}
  \end{equation}
  Additionally, we have the bounds
  \begin{equation}
    \label{eqn:bound-density-diffs}
    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}
    ~~ \mbox{and} ~~
    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}.
  \end{equation}
\end{lemma}
\noindent
See Section~\ref{sec:proof-derivative-bounds} for a proof.

@@

For shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
P_\theta$, and let $p_n, p$ be shorthand for the p.m.f.s of the two
distributions.  For the sets $A_i$ we recall that $B_i = \indic{X_i \in
  A_i}$.  The random variables
\begin{equation*}
  W_{n,i} \defeq 2 \left(\sqrt{\frac{p_n}{p}}(B_i) - 1\right)
\end{equation*}
are with $P$-probability 1 well-defined, and by the
inequalities~\eqref{eqn:h-fourth}, we have
that
\begin{align}
  \lefteqn{\var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
    \le 
    C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
      + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \cdot \frac{h_n^4}{n^2}
    + C \frac{k^4 \lip^4(f)}{
      P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{h_n^8}{n^4}} \nonumber \\
  & \qquad\qquad\qquad\qquad\qquad \le 
  C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
  \cdot \frac{h_n^4}{n^2}
  + C \frac{k^4 \lip^4(f)}{
    P_\theta(A_i)^3 P_\theta(A_i^c)^3}
  \frac{h_n^8}{n^4}
  \label{eqn:var-wni-expansion}
\end{align}
whenever
\begin{equation*}
  \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
  \score_\theta(A_i^c)\}
  \le \frac{1}{4}
  ~~ \mbox{and} ~~
  \frac{k_i h_n^2}{n} \lip^2(f)
  \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
\end{equation*}
Now, we use
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
coupled with Lemma~\ref{lemma:derivative-bounds} to show that the summed
variances converge to zero.  Indeed, Lemma~\ref{lemma:derivative-bounds} and
inequality~\eqref{eqn:var-wni-expansion} give that
\begin{equation*}
  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  \le C \cdot
  \left[\frac{k_i^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i^4}{P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{1}{n^3}\right] \frac{1}{n},
\end{equation*}
where $C < \infty$ depends only on $\lip(f)$ and $h_n$ (both of which are
uniformly bounded) whenever
\begin{equation*}
  \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)} \frac{1}{n} \le
  \frac{1}{C}.
\end{equation*}
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}
thus implies that $\E[\score_\theta(B_i)] = 0$ and
\begin{equation}
  \label{eqn:summed-variances-to-zero}
  \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  \to 0.
\end{equation}

@@

Now, we write the log-likelihood ratio. We have
\begin{align*}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  & = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
  & = \sum_{i = 1}^n W_{n,i}
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
  + \half \sum_{i = 1}^n W_{n,i}^2 R(W_{n,i})
\end{align*}
where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
Using the Taylor expansions of $\sqrt{\cdot}$ and
Lemma~\ref{lemma:derivative-bounds}, we have
\begin{align}
  \nonumber
  \half W_{n,i}
  & = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}}
  \pm \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
  + \frac{h_n^2}{n} \score_\theta(B_i)^2
  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
  & = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}} +
  C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right|
  \label{eqn:max-wni-zero}
\end{align}
where $|C| < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
uniformly bounded. From Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} we get
\[
C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right| \to 0. 
\]
Consequently $\max_i W_{n,i} \to 0$, so that
\begin{equation}
  \label{eqn:almost-at-the-end}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
\end{equation}
